\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

---
title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "Title"

@@

  - name          : "Manuel Spitschan "
    affiliation   : "3"
    corresponding : yes   
    address       : ""
    email         : ""
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

@@

bibliography      : ["r-references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r flowchart, include=FALSE}
Flowchart1 <- grViz("digraph nicegraph{

@@

Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution. As a result, we tested both five factor and six factor solutions.

```{r fac.id, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.png')

@@

```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=}
#LB.factor <- sapply(LB, as.factor)
#correlations <- polychoric(LB.factor, correct = 0)

@@

In the five

@@

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution,  out.width="50%",  warning=FALSE'}
hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
abline(h =47, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

>>>>

---
title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "LEBA"

@@

@@

bibliography      : ["references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

---

@@

```{r flowchart, include=FALSE, out.height= "100%", out.width= "100%"}
Flowchart1 <- grViz("digraph nicegraph{

@@

Scree plot ( Fig\@ref(fig:facid)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution. As a result, we tested both five factor and six factor solutions.

```{r facid, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.png')

@@

```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#LB.factor <- sapply(LB, as.factor)
#correlations <- polychoric(LB.factor, correct = 0)

@@

@@

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
abline(h =47, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
